Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-03 paper/paper_new.tex
Updates from Overleaf

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means. This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network, and, further support empirical [*predicative] analysis [analytics?]. This paper reports specifically on research combining machine learning  and  image  informatics tools and techniques. A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help]. Key findings indicate z, y, z.
%for x, y, z, can we give some numbers? thinking on this.
Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning. This research has implications for leveraging the extensive collection of digitized scientific images stored in globally, accessible open repositories.
%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.

@@

\subsection{Automatic Metadata Generation}
Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse.

>>>>

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means. This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network, and, further support empirical [*predicative] analysis [analytics?]. This paper reports specifically on research combining machine learning  and  image  informatics tools and techniques. A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help]. Key findings indicate z, y, z.
%for x, y, z, can we give some numbers? thinking on this.
Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning. This research has implications for tens of thousands of digitized specimens stored in globally, accessible open repositories.
%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.

@@

\subsection{Automatic Metadata Generation}
Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)\cite{Exif}, the camera's technical metadata that is automatically captured and inserted into digital image files at the time of digitization. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse.
